\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2013-01-05 paper/mswp2012-proposal.tex
finished costs section

\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | p{2.5cm} | l |}
\hline
Member & Full-time / Part-time & Position & costs per hour & Duration & Overall costs \\
\hline
\hline
project manager & FT & manager & & start - end & \\
\hline
co-project manager &  FT & manager & & start - end  & \\
\hline
quality manger & FT & manager & & start - end  & \\
\hline
strategy memeber 4 & FT &  middle-manager & & start with version 1.0  & \\
\hline
strategy memeber 4 & FT &  middle-manager &  & start with version 1.0  & \\
\hline
reserarcher 1 &  FT  & & & start - end   & \\
\hline
reserarcher 2 & FT  & & & start - end  & \\
\hline
reserarcher 3 & PT & & & start - end  & \\
\hline
reserarcher 4 & PT & & & middle - end & \\
\hline
reserarcher 5 & PT & & & middle - end &  \\
\hline
security expert & FT & & & start - end &  \\ 
\hline
usability \& design engineer 1 + 2 & FT & & & start - end  & \\
\hline
web dev 1 & FT & & & dev \& update & \\
\hline
web dev 2 & FT & &  & dev \& update & \\
\hline
web dev 3 & FT & &  & dev & \\
\hline
web dev 4 & FT & &  & dev & \\
\hline
mobile dev 1 & FT & &  & dev \& update & \\
\hline
mobile dev 2 & FT & &  & dev \& update & \\
\hline
mobile dev 3 & FT & &  & dev & \\
\hline
mobile dev 4 & FT & &  & dev & \\
\hline
\end{tabular}

\subsection{Equipment}
Workplace with licenses consisting of:

\begin{itemize}
	\item {Computer}
	\item {Maus}
	\item {Tastatur}
	\item {Betriebssystem}
	\item {IDE}
	\item {...}
\end{itemize}
Makes around \EUR{1500} - \EUR{2000}  per employee. \\

\subsection{Material}
Once:\\
Printer in the Office 3 $\times$ \EUR{1500} \\
Testing devices (Android phones and iPhones) 4 $\times$ \EUR{500} \\
Books for research and development about \EUR{500} \\
Notebooks for managers 5 $\times$ \EUR{800} \\
\\
Monthly:\\
Server \EUR{50} by renting mailserver, fileserver and repository \\
Internet \EUR{50} \\
\\

\subsection{Travel}

%hm, wieviele reisen sind nötig?

\subsection{Miscellaneous}

%--miete: 500€ monatlich? keine ahnung, wo liegen die preise?
%--strom, 
%telefon, 
%wasser, 
%heizung im büro
%werbekosten für die gewinnung dre nutzer und partner: folder und sowas
%befragung: vorbereitung, nen ort für die durchführung, die personen die teilnehmen sollten ne kleinigkeit bekommen, auswertung

>>>>

Members take from human resources chapter \ref{sect:team}.\\
\\
\begin{tabular}{| p{3.5cm} | p{2cm} | p{3cm} | p{2.5cm} | r |}
\hline
Member & Full-time / Part-time & Position & Duration & Overall costs \\
\hline
\hline
Project manager & FT & manager & start - end & \EUR{140.000} \\
\hline
Co-project manager &  FT & manager & start - end  & \EUR{130.000} \\
\hline
Quality manager & FT & manager & start - end  & \EUR{130.000} \\
\hline
Marketing manager 1 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
\hline
Marketing manager 2 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
\hline
Researcher 1 &  FT  & employee & start - end  & \EUR{80.000} \\
\hline
Researcher 2 & FT  & employee & start - end  & \EUR{80.000} \\
\hline
Researcher 3 & PT & employee & start - end  & \EUR{40.000} \\
\hline
Researcher 4 & PT & employee & middle - end & \EUR{20.000} \\
\hline
Researcher 5 & PT & employee & middle - end & \EUR{20.000}  \\
\hline
Security expert & FT & expert & start - end & \EUR{130.000}  \\ 
\hline
Usability- \& Design engineer 1 & FT & employee & start - end  & \EUR{80.000} \\
\hline
Usability- \& Design engineer 2  & FT & employee & start - end  & \EUR{80.000} \\
\hline
Web dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
\hline
Web dev 2 & FT & employee & dev \& update & \EUR{60.000} \\
\hline
Web dev 3 & FT & employee & dev & \EUR{40.000} \\
\hline
Web dev 4 & FT & employee & dev & \EUR{40.000} \\
\hline
Mobile dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
\hline
Mobile dev 2 & FT & employee & dev \& update & \EUR{60.000}  \\
\hline
Mobile dev 3 & FT & employee & dev & \EUR{40.000} \\
\hline
Mobile dev 4 & FT & employee & dev & \EUR{40.000} \\
\hline
\end{tabular}
\\
\\
Overall costs for personal: \EUR{1.454.000}

\subsection{Equipment}

About 22 Workstations.
\begin{itemize}
		\item{Computer}
		\item{Maus}
		\item{Keyboard}
		\item{Two Displays}
		\item{OS (License)}
		\item{IDE (License)}
		\item{Office (License)}
\end{itemize} 
	\begin{tabular}{| p{2cm} | p{6cm} | r |}
		\hline
		Workstation & Member & Costs \\
		\hline
		\hline
		01 & project manager   & \EUR{1.200} \\
		\hline
		02 & co-project manager  & \EUR{1.200} \\
		\hline
		03 & quality manger  & \EUR{1.500} \\
		\hline
		04 & marketing manager 1 & \EUR{1.200} \\
		\hline
		05 & marketing manager 2 & \EUR{1.200} \\
		\hline
		06 & researcher 1 &  \EUR{1.200} \\
		\hline
		07 & researcher 2 &  \EUR{1.200} \\
		\hline
		08 & researcher 3 &  \EUR{1.200} \\
		\hline
		09 & researcher 4 &  \EUR{1.200} \\
		\hline
		10 & researcher 5 &  \EUR{1.200} \\
		\hline
		11 & security expert  &  \EUR{1.800} \\
		\hline
		12 & usability \& design engineer 1 & \EUR{2.000} \\
		\hline
		13 & usability \& design engineer 2 & \EUR{2.000} \\
		\hline
		14 & web dev 1 &  \EUR{1.500} \\
		\hline
		15 & web dev 2 &  \EUR{1.500} \\
		\hline
		16 & web dev 3 &  \EUR{1.500} \\
		\hline
		17 & web dev 4 &  \EUR{1.500} \\
		\hline
		18 & mobile dev 1 &  \EUR{1.500} \\
		\hline
		19 & mobile dev 2 &  \EUR{1.500} \\
		\hline
		20 & mobile dev 3 &  \EUR{1.500} \\
		\hline
		21 & mobile dev 4 &  \EUR{1.500} \\
		\hline
		22 &  spare & \EUR{1.500} \\
		%&  &  \\
		\hline
	\end{tabular}
\\
\\
Total costs for equipment: \EUR{30.400}.

\subsection{Material}
\begin{tabular}{| p{4cm} | p{2cm} | p{2cm} | p{2cm} | r |}
	\hline
	Name & Amount & Preparation & Monthly & Overall \\
	\hline
	\hline
	Testing devices & 4 & \EUR{500} & 0 & \EUR{2.000} \\
	\hline
	Books (research, dev) & budget & \EUR{500} & 0 & \EUR{500}\\
	\hline
	Manager notebooks  & 5 & \EUR{800} & 0 & \EUR{4.000} \\
	\hline
	Laserprinter & 1 & \EUR{1500} & 0 & \EUR{1.500}  \\
	\hline
	Photoprinter & 1 & \EUR{500} & 0 & \EUR{500}  \\
	\hline
	Copystation \& Scanner & 1 & \EUR{1000} & 0 & \EUR{1.000}  \\
	\hline
	Server & 1 &  \EUR{200} &  \EUR{50} &  \EUR{1.600}   \\
	\hline
\end{tabular}
\\
\\
Total costs for material: \EUR{11.100}. \\
\\
Runtime of the whole project is 28 months. Therefore monthly for the server is 28 time \EUR{50}. \\
\\
Hosted server with functionalities:
\begin{itemize}
	\item{Mailing}
	\item{Fileserver}
	\item{Webserver}
	\item{Database}
	\item{Repository}
	\item{Ticket-System (Bugtracker)}
\end{itemize}
\subsection{Travel}
Given are the pool sizes of money for a specific task.\\
\begin{tabular}{| p{4cm} | r |}
	\hline
	Type & Cost \\
	\hline
	\hline
	Interview & \EUR{15.000} \\
	\hline
	Advertisement & \EUR{50.000} \\
	\hline
	Recruitment of partners & \EUR{35.000} \\
	\hline
\end{tabular}
\\
\\
Total costs travel: \EUR{100.000}.
\subsection{Miscellaneous}
\begin{tabular}{| p{4cm} | p{2cm} | p{2cm} | r |}
	\hline
	name & preparation & monthly & overall \\
	\hline
	\hline
	Internet \& Telephone &  \EUR{50} &  \EUR{50} & \EUR{1.450}  \\
	\hline
	Rent & \EUR{0} & \EUR{1.800} & \EUR{50.400} \\
	\hline
	Furnishment & \EUR{15.000} & \EUR{0} & \EUR{15.000} \\
	\hline
	Flyer, Folders & \EUR{0} & \EUR{200} & \EUR{5.600} \\
	\hline
\end{tabular}
\\
\\
Total costs for miscellaneous: \EUR{72.450}.\\
\\
Rent calculation is given by a space consumption of 8 $m^2$ for the first employee and 6 $m^2$ for every following one.\\
This gives us a total needed space of 130 $m^2$.

\subsection{Overall listing}

\begin{tabular}{| p{4cm} | r |}
	\hline
	Area & Costs \\
	\hline
	\hline
	Personal & \EUR{1.454.000}  \\
	\hline
	Equipment & \EUR{30.400} \\
	\hline
	Material & \EUR{11.100} \\
	\hline
	Travel & \EUR{100.000}\\
	\hline
	Miscellaneous & \EUR{72.450}\\
	\hline
	\hline
	Overall Project & \EUR{1.667.950} \\
	\hline
\end{tabular}
